The effects of varying depth in cosmic shear surveys

### 2019-10-18 paperdraft.tex
added new explanation for discrepancy

\section{Additional Figures and Tables}
\begin{table}[h]
\centering
\caption{Limiting magnitudes for the ten quantiles}
\label{tab:maglim}
\begin{tabular}{r c}
\hline\hline
quantile & $r$-band depth \\
\hline
0 & 25.76 \\
10 & 26.06 \\
20 & 26.15 \\
30 & 26.19 \\
40 & 26.23 \\
50 & 26.27 \\
60 & 26.31 \\
70 & 26.34 \\
80 & 26.39 \\
90 & 26.44 \\
100 & 26.60 \\
\hline
\end{tabular}
\end{table}
\begin{figure}[h]
\centering
\includegraphics[width=0.9\linewidth]{images/xis_all_cutoff.pdf}
\caption{The same Figure as Fig.~\ref{fig:all_xis}, but in this case the redshift distributions $p_n^i(z)$ were set equal to zero for $z>2$ in the models to mimick the redshift-cutoff in the mocks.}
\label{fig:redshift_cutoff}
\end{figure}
\begin{figure}[h]
\centering
\includegraphics[width=0.9\linewidth]{images/compare_cosmos.pdf}
\caption{Correction to the correlation functions in varying cosmologies. Depicted here are three flat sample cosmologies, where values within the 98\% CL of the KV450 survey were sampled.}
\label{fig:comparecosmo}
\end{figure}
\end{appendix}
\end{document}
%

>>>>

\section{Additional Figures and Tables}
\begin{table}[h]
\centering
\caption{Limiting magnitudes for the ten quantiles}
\label{tab:maglim}
\begin{tabular}{r c}
\hline\hline
quantile & $r$-band depth \\
\hline
0 & 25.76 \\
10 & 26.06 \\
20 & 26.15 \\
30 & 26.19 \\
40 & 26.23 \\
50 & 26.27 \\
60 & 26.31 \\
70 & 26.34 \\
80 & 26.39 \\
90 & 26.44 \\
100 & 26.60 \\
\hline
\end{tabular}
\end{table}
\begin{figure}[h]
\centering
\includegraphics[width=0.9\linewidth]{images/xis_all_cutoff.pdf}
\caption{The same Figure as Fig.~\ref{fig:all_xis}, but in this case the redshift distributions $p_n^i(z)$ were set equal to zero for $z>2$ in the models to mimick the redshift-cutoff in the mocks. Any residual differences are explained by the sub-pointing depth variations that are accounted for in the mocks, but not in the models. These variations slightly reduce the effect of varying depth.}
\label{fig:redshift_cutoff}
\end{figure}
\begin{figure}[h]
\centering
\includegraphics[width=0.9\linewidth]{images/compare_cosmos.pdf}
\caption{Correction to the correlation functions in varying cosmologies. Depicted here are three flat sample cosmologies, where values within the 98\% CL of the KV450 survey were sampled.}
\label{fig:comparecosmo}
\end{figure}
\end{appendix}
\end{document}
%
